Safe Memory Regions for Big Data Processing

### 2016-10-20 paper/overview2.tex
minor changes

\paragraph{Object Allocation} The ``\C{new@R T()}'' construct creates
a new object of type \C{T} in the region \C{R}. The specification of
the allocation region \C{R} in this construct is optional.  At
runtime, \name maintains a stack of \emph{active} regions, and we
refer to the region at the top of the stack as the \emph{allocation
context}. The statement \C{new T()} allocates the newly created object
in the current allocation context.
%
This is important as it enables \name applications to use existing
region-oblivious C\# libraries. In particular, given a  C\# library
function \C{f} (that makes no use of \name's region constructs), the
statement ``\C{letregion R \{ f(); \}}'' invokes \C{f}, but has the
effect that all objects allocated by this invocation are allocated in
the new region \C{R}.

@@

>>>>

\paragraph{Object Allocation} The ``\C{new@R T()}'' construct creates
a new object of type \C{T} in the region \C{R}. The specification of
the allocation region \C{R} in this construct is optional.  At
runtime, \name maintains a stack of \emph{active} regions, and we
refer to the region at the top of the stack as the \emph{allocation
context}. The statement \C{new T()} allocates the newly created object
in the current allocation context.
%
This is important as it enables \name applications to use existing
region-oblivious C\# libraries, as explained soon.

%In particular, given a  C\# library
%function \C{f} (that makes no use of \name's region constructs), the
%statement ``\C{letregion R \{ f(); \}}'' invokes \C{f}, but has the
%effect that all objects allocated by this invocation are allocated in
%the new region \C{R}.

@@

Opening a region also makes it the current allocation context.
Thus, given a  C\# library function \C{f} (that makes no use of \name's region constructs),
opening a region \C{R} and invoking \C{f} has the effect that all objects created by this
invocation are allocated in the region \C{R}.
